Differentially Private Bayesian Inference

### 2018-04-13 main.tex
update algorithm setting up

\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
\label{sec_bayesInfer}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_3)$.

@@

\subsection{Accuracy Study of Algorithms}
\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 200$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
  \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
    \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
\caption{The experimental results of accuracy of four algorithms}
\label{fig_data}
\end{center}
\end{figure*}

>>>>

\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
\label{sec_bayesInfer}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_3)$. Columns of the data set is corresponding to the number of parameters in Dirichlet distribution. The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the number of $1$ at the column $i$.

@@

\subsection{Accuracy Study with Hellinger Distance}
\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 200$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
  \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
    \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
\caption{The experimental results of accuracy of four algorithms}
\label{fig_data}
\end{center}
\end{figure*}
